Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-01 paper_intersections.tex
Intersections between components.

\subsection{Intersections between component meshes}
\label{sec:components}

>>>>

\subsection{Intersections between component meshes}
\label{sec:components}
We consider here the situation that components are in the interior of 3D bulk mesh. After we compute
all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
If the bulk element intersects more than one component element, than we can create candidates from these.

Let us start with description of how we store the intersection results, which will be of great importance here.
For each element intersection, we save the following data: reference to component and bulk element, barycentric coordinates on both and index of the component. These objects are stored in separate vectors for each pair 
of dimensions. Further we define a matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, and references to the actual intersection data.

The algorithm for 2d-2d intersections goes as follows. We iterate over all 2d-3d intersections, respectively over
the bulk elements having some intersections with 2d components. We look at the intersection map at the
bulk element row and collect all elements that have 2d-3d intersection with it.
Now comes in play the component number $\gamma$. If $\gamma$ is equal for both component elements, then 
these are part of a single continuous component and we do not compute any intersection.
Otherwise we obtain a new candidate pair, for which IP can be computed.

The algorithm for 1d-2d is analogical, only we do not have to check the component number.
Note that this way, we do not obtain any intersection in the exterior of bulk mesh.
If such problem is of our interest, we find the candidate pairs using the search algorithms as in
initialization phase of advancing front method.
